Verifying Demonstrations

### 2017-08-04 properties.tex
Some more editing
Syncs conclusions with previous edits

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.
They must also be able to verify that each proof is indeed related to the 
event.
We must associate the proof to the event both spatially (the correct location) 
and temporally (it is related to the time-interval of the event).
We can essentially divide it into the following requirements:
\begin{frame}
\begin{requirements}[\ref*{EligibilityVerif}.]
  \item\label{UniqueIndividual} Prove that the data is unique for an 
    individual.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}
\end{frame}

\Cref{UniqueIndividual} is required to prevent Sybil attacks.
I.e.\ that one individual can provide two proofs of participation and thus be 
counted twice, this situation should be detectable.

@@

\begin{frame}<presentation>
  \begin{idea}[V\ref{EligibilityVerif} Eligibility]
    \begin{itemize}
      \item Must verify that the proof is not reused from before 
        (A\ref{CreatedAfterStart} and A\ref{CreatedBeforeEnd}).
      \item Must verify that each proof belongs to a unique individual (not 
        only Sybil).
    \end{itemize}
  \end{idea}
\end{frame}

>>>>

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.
They must also be able to verify that each proof is indeed related to the 
event.
We must associate the proof to the event both spatially (the correct location) 
and temporally (it is related to the time-interval of the event).
We can essentially divide it into the following requirements:
\begin{frame}
\begin{requirements}[\ref*{EligibilityVerif}.]
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}
\end{frame}

\Cref{CountOnce} is required to prevent Sybil attacks.
I.e.\ that one individual can provide two proofs of participation and thus be 
counted twice, this situation should be detectable.

@@

\begin{frame}<presentation>
  \begin{idea}[V\ref{EligibilityVerif} Eligibility]
    \begin{itemize}
      \item Must verify that the proof is not reused from before.
      \item Must verify that each proof belongs to a unique individual (not 
        only Sybil).
    \end{itemize}
  \end{idea}
\end{frame}
